\chapter{Requirements} % Jake [DONE]

\section{Functional Requirements}
    \subsection{Critical}
        \begin{itemize}
            \item The system will function on iOS devices using Google Cardboard.
            \item The system will inform the user right after it detects that the user is stressed.
            \item The system will train users in emotional resilience.
            \item 	The system will keep track of users' personal progress.
            \item The system will collect user data anonymously (including personal progress).
            \item The system will measure user heart rate using the phone's camera lens.
            \item The system will adjust difficulty of the game, based on how well the individual handles stress and his/her stress level.
\end{itemize}
    \subsection{Recommended}
        \begin{itemize}
            \item The VR experience will contain spatialized audio.
            \item The VR experience will halt if the user is too uncomfortable. 
            \item Users' data will be sent for research, with their consent.
        \end{itemize}
    \subsection{Suggested}
        \begin{itemize}
            \item The system will function on Android devices.
        \end{itemize}
\section{Non-Functional Requirements}
    \subsection{Critical}
        \begin{itemize}
            \item The application will be user-friendly.
            \item The VR experience will be immersive.
            \item The VR experience will be a maximum of 2 minutes long.
            \item The system will be able to change the difficulty of the game in real time based on the user's performance.
        \end{itemize}
    \subsection{Recommended}
        \begin{itemize}
            \item The system will be supportive of multiple languages.
            \item The application will be energy efficient.
        \end{itemize}
    \subsection{Suggested}
        \begin{itemize}
            \item The system will be maintainable and portable.
        \end{itemize}
\section{Design Constraints}
\begin{itemize}
\item 	Compliance to applicable laws, regulations and standards
\item 	Style guide
\item 	Sensory Design
\item 	Usability principles, frameworks and standards
\item 	Design principle
\item 	Integration
\end{itemize}
     
     