\chapter{Test Plan} \label{test-plan} % Jake [DONE]
% see 101718.pdf in COEN 174 notes
Testing is fundamental for ensuring that our product works effectively for its users. Throughout this project, we will utilize testing to verify our product works and validate that we were building the right product. 

\section{White Box Testing}

As we develop this project, we will be constantly testing and debugging our solution. Since we are using GitHub for reasons mentioned in Section~\ref{tech-used}, this will simplify deploying our system and verifying if changes are functioning correctly.

\subsection{Unit Testing}
    We will divide our functionality into modules to implement unit testing. We will create a testing directory that includes test cases for each of these respective modules.
\subsection{Integration Testing}
    After unit testing is complete, we will incorporate multiple modules to test together. We will test to verify our navigation functionality, allowing for a more seamless experience for black box testers.
\section{Black Box Testing}

Prior to beginning black box testing, we will need to receive permission from the SCU Institutional Review Board to conduct research with human participants.
% https://www.scu.edu/provost/research/research-compliance-and-integrity/human-subjects/
\subsection{System Testing}
    We will enlist testers to test the integrated system to evaluate the system’s compliance with our specified requirements. They will test our mobile application on different hardware to ensure portability.
\subsection{Acceptance Testing}
    For our final phase of testing, we will test with parents enrolled in Dr. Burn's Resilient Families Program.